Random Forests", OAs

### 2024-01-05 src/oa_RF.Rmd
refined model OA

# There are no lags for 1996, so it is removed
df <- df %>% filter(year > 1996) %>% 
  dplyr::select(oa11cd, year, RGN11CD, n, n.l.slag, n.nearest.city.lag, n.nearest.retail.lag, n.London.lag, London, dist, dist.retail) #growth, abs.growth, RGN11NM,

@@

# df %>% dplyr::select(area, dist, dist.retail, London, south, n.slag, n.lag, n.l.slag, n.nearest.city, year) %>% 
#   #sapply(function(x) sum(is.na(x)))
#   summarise(across(where(is.numeric), .fns = 
#                      list(#n = is.na,
#                           min = min,
#                           median = median,
#                           mean = mean,
#                           stdev = sd,
#                           # q25 = ~quantile(., 0.25),
#                           # q75 = ~quantile(., 0.75),
#                           max = max))) %>%
#   pivot_longer(everything(), names_sep='_', names_to=c('variable', '.value'))
# 
# df %>% dplyr::select(n.London.lag, n.nearest.city.lag, n.nearest.retail.lag, n.l.slag, year, London, dist, dist.retail) %>% 
#   #sapply(function(x) sum(is.na(x)))
#   summarise(across(where(is.numeric), .fns = 
#                      list(#n = is.na,
#                           min = min,
#                           median = median,
#                           mean = mean,
#                           stdev = sd,
#                           # q25 = ~quantile(., 0.25),
#                           # q75 = ~quantile(., 0.75),
#                           max = max))) %>%
#   pivot_longer(everything(), names_sep='_', names_to=c('variable', '.value'))

>>>>

# There are no lags for 1996, so it is removed
df <- df %>% filter(year > 1996) %>% 
  dplyr::select(oa11cd, year, RGN11CD, n, abs.growth, n.l.slag, n.nearest.city.lag, n.nearest.retail.lag, n.London.lag, London, dist, dist.retail) #growth, abs.growth, RGN11NM,

@@

# df %>% dplyr::select(area, dist, dist.retail, London, south, n.slag, n.lag, n.l.slag, n.nearest.city, year) %>% 
#   #sapply(function(x) sum(is.na(x)))
#   summarise(across(where(is.numeric), .fns = 
#                      list(#n = is.na,
#                           min = min,
#                           median = median,
#                           mean = mean,
#                           stdev = sd,
#                           # q25 = ~quantile(., 0.25),
#                           # q75 = ~quantile(., 0.75),
#                           max = max))) %>%
#   pivot_longer(everything(), names_sep='_', names_to=c('variable', '.value'))
# 
# df %>% dplyr::select(n, n.London.lag, n.nearest.city.lag, n.nearest.retail.lag, n.l.slag, year, London, dist, dist.retail) %>%
#   #sapply(function(x) sum(is.na(x)))
#   summarise(across(where(is.numeric), .fns =
#                      list(#n = is.na,
#                           min = min,
#                           median = median,
#                           mean = mean,
#                           stdev = sd,
#                           # q25 = ~quantile(., 0.25),
#                           # q75 = ~quantile(., 0.75),
#                           max = max))) %>%
#   pivot_longer(everything(), names_sep='_', names_to=c('variable', '.value'))
# 
# df %>% slice_max(order_by = n, n = 5, by = year)
```
